Dynamic Transition Analysis with TIMES

### 2020-09-18 doc/2020-03-paper/Appendix.tex
added better figures
Former-commit-id: b18df403e5dca39364eff007f47d536a239a0b42
Former-commit-id: c1a0964fe287ada31a822f00e42bbfcad6b2d9ad

\section{Data and assumptions for scenarios} \label{Appendix}

@@

\begin{table}[!ht]
	\caption{Initial condition CO$_2$ emissions compared to the model and data from the Carbon Trust\cite{carbon_brief_carbon_2018}.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.08\textwidth} p{0.35\textwidth} p{0.35\textwidth} p{0.15\textwidth}}
		\hline
\textbf{Year} & \textbf{Model Emissions} & \textbf{Actual Emissions} & \textbf{Error} \\
  & Mt CO$_2$-eq. & Mt CO$_2$-eq. &  \\
\hline
2013 & 603.62 & 592.4 & 1.89 \% \\
2014 & 582.27 & 572.6 & 1.69 \% \\
2015 & 572.53 & 560.3 & 2.18 \% \\
2016 & 565.94 & 552.8 & 2.38 \% \\
\hline 
	\end{tabularx}
\label{ic-co2}
\end{table}

@@

\gls{USC} \cite{eia_cost_2020,ipcc_2014} & 3661 & 40.41 & 0.045 & 40 & CF=0.55 & 820 & 2017 \\
\gls{lng}\cite{eia_cost_2020,ipcc_2014} & 1079 & 14 & 0.0025 & 30 & CF=0.55 & 490 & 2017 \\
Nuclear \cite{eia_cost_2020,ipcc_2014,lokhov_load-following_2011} & 6317 & 121.13 & 2.36 & 60 & CF=0.6-0.95 & 12 & 2017 \\

@@

Solar \cite{eia_cost_2020,ipcc_2014} & 1307(2017) & 15.19 & 0  & 25 & CF=0.14 & 37 & 2017 \\

@@

\cite{eia_cost_2020,ipcc_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016} & 2406(2050) &  &  &  & CF=0.35(2050) & 7 (2040) &  \\

@@

\cite{eia_cost_2020,ipcc_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016} & 3381(2050) &  &  & & CF=0.40(2050) & 11(2050) &  \\

@@

\cite{eia_cost_2020,ipcc_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016} & 5610(2050) &  &  &  & CF=0.45(2050) & 11(2050) &  \\

@@

 \cite{eia_cost_2020,ipcc_2014} & 1422(2050) &  & &  &  &  & \\

@@

 \cite{eia_cost_2020,ipcc_2014} & 4091(2050) &  &  &  &  &  & \\

@@

>>>>

\section{Model data, assumptions, and secondary results} \label{Appendix}

@@

\begin{table}[!ht]
	\caption{Initial condition CO$_2$ emissions compared to the model and data from the Carbon Trust\cite{carbon_brief_carbon_2018}.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.08\textwidth} p{0.35\textwidth} p{0.35\textwidth} p{0.15\textwidth}}
\textbf{Year} & \textbf{Model Emissions} & \textbf{Actual Emissions} & \textbf{Error} \\
  & Mt CO$_2$-eq. & Mt CO$_2$-eq. &  \\
2013 & 603.62 & 592.4 & 1.89 \% \\
2014 & 582.27 & 572.6 & 1.69 \% \\
2015 & 572.53 & 560.3 & 2.18 \% \\
2016 & 565.94 & 552.8 & 2.38 \% \\
	\end{tabularx}
\label{ic-co2}
\end{table}

@@

\gls{USC} \cite{eia_cost_2020,ipcc_climate_2014} & 3661 & 40.41 & 0.045 & 40 & CF=0.55 & 820 & 2017 \\
\gls{lng}\cite{eia_cost_2020,ipcc_climate_2014} & 1079 & 14 & 0.0025 & 30 & CF=0.55 & 490 & 2017 \\
Nuclear \cite{eia_cost_2020,ipcc_climate_2014,lokhov_load-following_2011} & 6317 & 121.13 & 2.36 & 60 & CF=0.6-0.95 & 12 & 2017 \\

@@

Solar \cite{eia_cost_2020,ipcc_climate_2014} & 1307(2017) & 15.19 & 0  & 25 & CF=0.14 & 37 & 2017 \\

@@

\cite{eia_cost_2020,ipcc_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016,bonou_life_2016} & 2406(2050) &  &  &  & CF=0.35(2050) & 7 (2040) &  \\

@@

\cite{eia_cost_2020,ipcc_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016,bonou_life_2016} & 3381(2050) &  &  & & CF=0.40(2050) & 11(2050) &  \\

@@

\cite{eia_cost_2020,ipcc_climate_2014,kato_energy_2016,govindji_appraisal_2012,heger_wind_2016,bonou_life_2016} & 5610(2050) &  &  &  & CF=0.45(2050) & 11(2050) &  \\

@@

 \cite{eia_cost_2020,ipcc_climate_2014} & 1422(2050) &  & &  &  &  & \\

@@

 \cite{eia_cost_2020,ipcc_climate_2014} & 4091(2050) &  &  &  &  &  & \\

@@

\begin{figure}[h] 
\centering
\hspace*{-3cm}
\includegraphics[scale=0.07]{figures/useless}
\caption{Sensitivity analysis results for \gls{PEMFC} and \gls{CCS} coal.}
\label{sa-useless}
\end{figure}

### 2020-09-18 doc/2020-03-paper/discussion.tex
added better figures
Former-commit-id: b18df403e5dca39364eff007f47d536a239a0b42
Former-commit-id: c1a0964fe287ada31a822f00e42bbfcad6b2d9ad

%renewables and flexibility
In all scenarios, solar and wind supply a large part of the electricity demand. Unless large numbers of nuclear power plants are constructed, Japan must also invest in offshore wind farms by 2030 (Figs. \ref{scen1,scen3,scen4,scen5}). If hydrogen and CCS are not deployed by 2035, investment in offshore floating turbines may also necessary (\ref{scen1}). With such a large share of renewables, grid flexibility is extremely important. This requires significant investment in storage technologies, and ensuring that all emerging technologies are flexible and responsive. As natural gas is the only extant option for load-following, it is important to incorporate nuclear as in Scenarios 2 and 4 (Figs. \ref{scen2} and \ref{scen4}), or invest heavily in hydrogen (\ref{scen3} and \ref{scen5} to achieve emission cuts while simultaneously keeping natural gas operational for load-following. Additionally, nuclear power plants and CCS power plants must be able to load-follow, or be coupled to storage, ideally electrolysers, in order to store their excess electricity for peak demand. Any fuel cell technology utilized must also be extremely flexible and responsive. Since our model prefers \gls{SOFC}s to \gls{PEMFC}s due to their higher efficiency, it is important that \gls{SOFC}s reduce their startup times to have an edge over \gls{PEMFC}s in utility-scale applications.

%batteries
Lithium ion is the preferred storage medium in the absence of hydrogen. However, as the base case scenarios indicate, extremely large capacities of storage must be deployed to achieve a stable grid that can sustain the large capacities of renewables required for deep emission cuts. While lithium and cobalt may be available, cobalt and manganese reserves are limited \cite{scrosati_lithium-ion_2011,simon_potential_2015,turcheniuk_ten_2018} , which may inflate the prices of lithium ion storage if it is relied upon as the primary storage medium. It may be preferable to redesign batteries to reduce the amount of rare minerals used in their manufacturing, and improve recycling to increase the recovery rate of rare metals. The life cycle emissions from batteries must also be reduced by using cleaner materials and electricity for manufacturing. If hydrogen storage is available, battery storage storage serves as a near-term transition technology after which hydrogen storage dominates (\ref{scen3,scen4,scen5}).

>>>>

%renewables and flexibility
In all scenarios, solar and wind supply a large part of the electricity demand. Unless large numbers of nuclear power plants are constructed, Japan must also invest in offshore wind farms by 2030 (Figs. \ref{scen1},\ref{scen3}-\ref{scen5}). If hydrogen and CCS are not deployed by 2035, investment in offshore floating turbines may also necessary (\ref{scen1}). With such a large share of renewables, grid flexibility is extremely important. This requires significant investment in storage technologies, and ensuring that all emerging technologies are flexible and responsive. As natural gas is the only extant option for load-following, it is important to incorporate nuclear as in Scenarios 2 and 4 (Figs. \ref{scen2} and \ref{scen4}), or invest heavily in hydrogen (\ref{scen3} and \ref{scen5} to achieve emission cuts while simultaneously keeping natural gas operational for load-following. Additionally, nuclear power plants and CCS power plants must be able to load-follow, or be coupled to storage, ideally electrolysers, in order to store their excess electricity for peak demand. Any fuel cell technology utilized must also be extremely flexible and responsive. Since our model prefers \gls{SOFC}s to \gls{PEMFC}s due to their higher efficiency, it is important that \gls{SOFC}s reduce their startup times to have an edge over \gls{PEMFC}s in utility-scale applications.

%batteries
Lithium ion is the preferred storage medium in the absence of hydrogen. However, as the base case scenarios indicate, extremely large capacities of storage must be deployed to achieve a stable grid that can sustain the large capacities of renewables required for deep emission cuts. While lithium and cobalt may be available, cobalt and manganese reserves are limited \cite{scrosati_lithium-ion_2011,simon_potential_2015,turcheniuk_ten_2018} , which may inflate the prices of lithium ion storage if it is relied upon as the primary storage medium. It may be preferable to redesign batteries to reduce the amount of rare minerals used in their manufacturing, and improve recycling to increase the recovery rate of rare metals. The life cycle emissions from batteries must also be reduced by using cleaner materials and electricity for manufacturing. If hydrogen storage is available, battery storage storage serves as a near-term transition technology after which hydrogen storage dominates (\ref{scen3}-\ref{scen5}).

### 2020-09-18 doc/2020-03-paper/results.tex
adjusted figure sizes
Former-commit-id: 723ebece9a628c30d3a45cc8f4c7a86d323348be
Former-commit-id: 47cda099c10c589ad1f8afdd651f55678e5aa3c7
added better figures
Former-commit-id: b18df403e5dca39364eff007f47d536a239a0b42
Former-commit-id: c1a0964fe287ada31a822f00e42bbfcad6b2d9ad

@@

The fifth scenario's results (Fig. \ref{scen5}) closely resemble those of the third scenario (Fig. \ref{scen3}). However, \gls{SOEC}s rapidly replace a large fraction of aging \gls{PEMEC}s. Some \gls{PEMEC}s remain in the mix until 2100 despite their lower efficiency due to their lower cost. Both 2030 and 2050 emission targets are met, but no additional emission reductions occur beyond 2050. The amount of electricity diverted to storage technologies is 41,752 TWh, primarily from solar and emerging solar technologies(48\%), onshore wind (28\%), and fixed-bottom offshore wind (20\%). From this, 35,550 TWh of hydrogen is generated, mostly from \gls{SOEC} (56\%), \gls{PEMEC} (43\%). \gls{AEC} contributes a mere 0.95\% of the total hydrogen, and \gls{PWS} plays the smallest role at 0.05\%. The cost of this transition is \textbf{3,180,613 MUSD}.

\begin{figure}[htb] 
\centering
\vspace*{-3cm}
\includegraphics[scale=0.42]{figures/conv_nonuc}
\caption{Scenario 1 - Conventional technologies, no new nuclear.}
\label{scen1}
\end{figure}

\begin{figure}[h] 
\centering
\vspace*{-3cm}
\includegraphics[scale=0.42]{figures/conv_nuc}
\caption{Scenario 2 - Conventional technologies, with new nuclear.}
\label{scen2}
\end{figure}

\begin{figure}[h] 
\centering
\vspace*{-3cm}
\includegraphics[scale=0.41]{figures/newtechs_nonuc}
\caption{Scenario 3 - Emerging technologies, no new nuclear.}
\label{scen3}
\end{figure}

\begin{figure}[h] 
\centering
\vspace*{-3cm}
\includegraphics[scale=0.41]{figures/newtechs_nuc}
\caption{Scenario 4 - Emerging technologies, with new nuclear.}
\label{scen4}
\end{figure}

\begin{figure}[h] 
\centering
\vspace*{-3cm}
\includegraphics[scale=0.41]{figures/lowtrltech_nonuc}
\caption{Scenario 5 - Emerging technologies and nascent hydrogen technologies, no new nuclear.}
\label{scen5}
\end{figure}

@@

\begin{figure}[h] 
\centering
\hspace*{-3cm}
\includegraphics[scale=0.14]{figures/techs}
\caption{Sensitivity analysis of selected model parameters. Red dots indicate points that are zero values, while blue dots indicate non-zero values. Plots with a grey background represent false correlations with characteristics of technologies that were not deployed (i.e. PEM FC and CCS Coal). }
\label{sa-techs}
\end{figure}

\begin{figure}[h] 
\centering
\hspace*{-3cm}
\includegraphics[scale=0.14]{figures/syscost}
\caption{Sensitivity analysis of the model's overall transition cost between 2013-2100 with respect to selected model parameters.  Red dots indicate points that are zero values, while blue dots indicate non-zero values. Plots with a grey background represent false correlations with characteristics of technologies that were not deployed (i.e. PEM FC and CCS Coal).}
\label{sa-syscost}
\end{figure}

\begin{figure}[h] 
\centering
\hspace*{-3cm}
\includegraphics[scale=0.14]{figures/co2emi}
\caption{Sensitivity analysis of the model's cumulative emissions over 2013-2100 with respect to selected model parameters. Red dots indicate points that are zero values, while blue dots indicate non-zero values. Plots with a grey background represent false correlations with characteristics of technologies that were not deployed (i.e. PEM FC and CCS Coal). }
\label{sa-co2}
\end{figure}

>>>>

\begin{figure}[H] 
\centering
\vspace*{-3cm}
\includegraphics[scale=0.42]{figures/conv_nonuc}
\caption{Scenario 1 - Conventional technologies, no new nuclear.}
\label{scen1}
\end{figure}

\begin{figure}[H] 
\centering
\vspace*{-3cm}
\includegraphics[scale=0.42]{figures/conv_nuc}
\caption{Scenario 2 - Conventional technologies, with new nuclear.}
\label{scen2}
\end{figure}

\begin{figure}[H] 
\centering
\vspace*{-3cm}
\includegraphics[scale=0.41]{figures/newtechs_nonuc}
\caption{Scenario 3 - Emerging technologies, no new nuclear.}
\label{scen3}
\end{figure}

\begin{figure}[H] 
\centering
\vspace*{-3cm}
\includegraphics[scale=0.41]{figures/newtechs_nuc}
\caption{Scenario 4 - Emerging technologies, with new nuclear.}
\label{scen4}
\end{figure}

\begin{figure}[H] 
\centering
\vspace*{-3cm}
\includegraphics[scale=0.41]{figures/lowtrltech_nonuc}
\caption{Scenario 5 - Emerging technologies and nascent hydrogen technologies, no new nuclear.}
\label{scen5}
\end{figure}

@@

The fifth scenario's results (Fig. \ref{scen5}) closely resemble those of the third scenario (Fig. \ref{scen3}). However, \gls{SOEC}s rapidly replace a large fraction of aging \gls{PEMEC}s, starting from 2055. Some \gls{PEMEC}s remain in the mix until 2100 despite their lower efficiency due to their lower cost. Both 2030 and 2050 emission targets are met, but no additional emission reductions occur beyond 2050. The amount of electricity diverted to storage technologies is 41,752 TWh, primarily from solar and emerging solar technologies(48\%), onshore wind (28\%), and fixed-bottom offshore wind (20\%). From this, 35,550 TWh of hydrogen is generated, mostly from \gls{SOEC} (56\%), \gls{PEMEC} (43\%). \gls{AEC} contributes a mere 0.95\% of the total hydrogen, and \gls{PWS} plays the smallest role at 0.05\%. The cost of this transition is \textbf{3,180,613 MUSD}.

@@

\begin{figure}[H] 
\centering
\hspace*{-1cm}
\includegraphics[scale=0.09]{figures/pws}
\caption{Sensitivity analysis of Photochemical Water Splitting. Red dots indicate points that are zero values, while blue dots indicate non-zero values.}
\label{pws}
\end{figure}

\begin{figure}[H] 
\centering
%\hspace*{-3cm}
\includegraphics[scale=0.12]{figures/satechsh2}
\caption{Sensitivity analysis of hydrogen generation technologies \gls{SOEC} and \gls{PEMEC}}.
\label{satechs-h2}
\end{figure}

\begin{figure}[H] 
\centering
%\hspace*{-3cm}
\includegraphics[scale=0.12]{figures/satechselc}
\caption{Sensitivity analysis of electricity generation technologies \gls{SOFC} and \gls{CCS} gas.}
\label{satechs-elc}
\end{figure}

\begin{figure}[H] 
\centering
%\hspace*{-3cm}
\includegraphics[scale=0.15]{figures/syscost}
\caption{Sensitivity analysis of the model's overall transition cost between 2013-2100 with respect to selected model parameters.}
\label{syscost}
\end{figure}

\begin{figure}[H] 
\centering
%\hspace*{-3cm}
\includegraphics[scale=0.15]{figures/co2emi}
\caption{Sensitivity analysis of the model's cumulative emissions over 2013-2100 with respect to selected model parameters.}
\label{co2emi}
\end{figure}

Preliminary assessment of our sensitivity analysis data (Fig. \ref{sa-useless}) indicates that \gls{PEMFC}s are never utilized due to their efficiency being lower than that of \gls{SOFC}s, and \gls{CCS} coal plants are never deployed due to their high emission coefficient. \gls{PWS} plays a minor role in generating 0-20 TWh of hydrogen over the entire simulation's time-period (Fig. \ref{pws}), as opposed to \gls{SOEC}s which generate 19,500-22,500 TWh of hydrogen, and \gls{PEMEC}s, which generate 12,000-16,000 TWh. The share of \gls{PWS} was found to be strongly correlated to its investment cost, with \$3300/kW the approximate threshold at which this technology ceases to be deployed. It's deployment is also weakly correlated with the splitting efficiency, wherein values greater than 21\% seem most favourable for its deployment. The emission coefficient is too small to have an impact on the overall emissions from the system considering \gls{PWS}'s small deployment, hence it does not appreciably affect its deployment. Since \gls{PEMFC}s, \gls{CCS} coal, and \gls{PWS} are not deployed in quantities significant enough to affect the model's performance, they are omitted as potential dependent variables for the rest of the sensitivity analysis.

\gls{SOEC}'s share is most strongly correlated with their investment cost, however they play a non-trivial role over the range of perturbation applied to said parameter (Fig. \ref{satechs-h2}). Their deployment is largely insensitive to their emission coefficient as their cost and high efficiency trumps any increase in emissions due to their deployment, which will be negligible due to their small emission coefficient. \gls{PEMEC} (Fig. \ref{satechs-elc}) and \gls{SOFC} (Fig. \ref{satechs-elc}) deployment is also most noticeably affected by their respective investment costs. The share of \gls{CCS}-Gas (Fig. \ref{satechs-elc}) is relatively small, about 2-3\%, due to its emission coefficient being much larger than that of all hydrogen technologies. Its deployment is most strongly correlated with the investment cost of \gls{SOFC}s as a reduction in the deployment of fuel cells forces the model to marginally increase CCS Gas deployment to achieve its emission goals.

The final set of results (Fig. \ref{syscost} and \ref{co2emi}) indicate that system's total transition cost and total emissions are tightly correlated with the investment cost of \gls{SOFC}s. This follows from the large share of \gls{SOFC}s, and the fact that they are the most important technology in the model in terms of reducing emissions and converting excess power from renewables into electricity, yet they are the most expensive technology available to the model.
